---
title: "Data exploration"
format: html
editor: visual
---

```{r}
#install.packages("haven")
library(haven)
library(tidyverse)
```

```{r}
# Gathering data from .dta file
data <- read_dta("data/AJAE MS#19355-Data and Codes-Gatti/data.dta")

# Create CSV from data
write.csv(data, "irrigation_data.csv", row.names = FALSE)
```

```{r}
data <- read_csv(here::here("data", "irrigation_data.csv"))
```



```{r}

```

## 1. Data Description
#### After the code block(s) that read in and clean the data, add some notes covering:

-   What does each row represent? What is the unit of observation?
-   What are the key outcome, treatment, and control variables?
-   Any notable data cleaning decisions (dropped observations, constructed variables, etc.)
-   Sample size, time period, and geographic scope



```{r}

```

## 2. Annotated Replication
#### After each subsequent code block, add some notes covering:

-   What does the code accomplish? (summary of the procedure or model)
-   What is the causal identification approach? (e.g., DiD, RDD, IV, matching)
-   What assumptions must hold for the estimates to be causally valid?
-   Are there any signs in the output that those assumptions are or are not satisfied?


```{r}

```

## 3. Critical Evaluation
#### Somewhere in the write-up (or as a closing section), address each of the following:

Causal identification: Is the identification strategy credible? What would have to be true for the estimates to be causal?
Statistical assumptions: Are key assumptions (parallel trends, exclusion restriction, etc.) tested or defended? Do you find the evidence convincing?
Sampling & external validity: Who is in the sample? To whom can results be generalized?
Measurement: Are the outcome and treatment variables measured accurately and without systematic bias?
Other limitations: Anything else that affects how much weight you would put on the study’s conclusions?

